TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems

### 2017-02-03 ISORC2017/paper.tex
Update

Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.
TINET is a TCP/IP protocol stack for embedded systems.
Although TINET is a compact TCP/IP protocol stack, it consists of many complex source codes.
Therefore, it is difficult to maintain, extend, and analysis the software.

To improve the scalability and configurability, this paper has proposed a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
The component-based TINET provides software developers high productivity such as change of network buffer size and adding/removing TCP (or UDP) function.
We evaluate the component-based TINET compared with the original TINET.
We confirm that the overheads of execution time and memory consumption are low, and that the configurability is improved.

In this paper, we also demonstrates a use case of the dynamic component connection method of TECS with a network application.

@@

Internet of Things (IoT) is an essential keyword for the next era.
Such as wearable devices, smart devices, and smart homes, various things are connected to the Internet, enriching our lives.
Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
It is not practical to implement the same communication function as a general computer because embedded systems have several restrictions such as low memory capacity.

@@

Component-based development is an approach to improve software productivity.
Component-based development is a design technique that can be applied to reusable software development \cite{par:Crnkovic}\cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.
In addition, individual component diagrams enable the visualization of an entire system.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
This paper evaluates the overheads of execution time and memory consumption and the amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.

@@

    \item {\bf Improve configurability}\mbox{}\\
        TINET+TECS is a component-based system, therefore the software is flexible to change the configuration such as resizing network buffer, adding/removing TCP (or UDP) functions, and support both IPv4 and IPv6.
        In addition, a component diagram provides visualization of TINET, a complicated system.

    \item {\bf Dynamic connection method}\mbox{}\\

    \item {\bf Support legacy codes}\mbox{}\\
        TECS supports the adapter to call TECS functions from existing C codes, thus TINET+TECS can be applied to an existing application.
    % \item {\bf Software visualization}

@@

This section describes system model, including the basic technologies such as TINET and TECS.
System model of the proposed system is shown as Fig. \ref{fig:System Model}.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/SystemModel.pdf}
    \caption{System model}
    \label{fig:System Model}
\end{figure}

\subsection{TINET}

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
TINET has been released as open source.

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.
Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
% TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
Users transmit and receive the data using a Communication End Point (CEP) which is an interface like a socket.
In transmission process, headers are attached to the data body passed to the CEP at each protocol layer, and the data is transmitted from the network device.
In reception process, headers of the data body received in the network device are analyzed at each protocol layer, and the data is passed to the CEP.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/TINET_Hier.pdf}
    \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
    \label{fig:TINET_Hier}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/component_diagram.eps}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

@@

Fig.\ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees,
               [in] uint32_t speed_abs,
                [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
        In Fig. \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/ComponentProtocolStack.pdf}
    \caption{Component diagram of protocol stack}
    \label{fig:ComponentProtocolStack}
\end{figure}

\subsection{Memory allocator component}

\subsubsection{send/receive specifier}

TECS supports {\it send}/{\it receive} specifiers, which are interface specifiers \cite{par:RPC}.
TINET+TECS uses {\it send} and {\it receive} specifiers instead of {\it in} and {\it out} to reduce the number of copies.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start([send(sNetworkAlloc),size_is(size)]int8_t *outputp,
             [in]int32_t size,
             [in]uint8_t align);
  void read([receive(sNetworkAlloc),size_is(*size)]int8_t **inputp,
            [out]int32_t *size,
            [in]uint8_t align);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{An example of send and receive}
\label{src:SendReceive}
\end{figure}

\subsection{Network timer component}

\subsection{TECS Adapter}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/TECS_Adapter.pdf}
    \caption{TECS Adapter}
    \label{fig:TECS_Adapter}
\end{figure}

\section{Evaluation and Demonstration}
\label{sec:Evaluation and Demonstration}

@@

Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP}.

@@

@@

The authers would like to thank OO for supporting this research.
This work is supported by JSPS KAKENHI Grant Number 15H05305.

>>>>

Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.
TINET is a TCP/IP protocol stack for embedded systems.
Although TINET is a compact TCP/IP protocol stack, it consists of many complex source codes.
Therefore, it is difficult to maintain, extend, and analysis the software.
To improve the scalability and configurability, this paper has proposed TINET+TECS, a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
The component-based TINET provides software developers high productivity such as change of network buffer size and adding/removing TCP (or UDP) function.
We evaluate the component-based TINET compared with the original TINET.
We confirm that the overheads of execution time and memory consumption are low, and that the configurability is improved.

@@

Internet of Things (IoT) is an essential keyword for the next era \cite{par:IoTIndustries} \cite{par:IoTComputing}.
Various things, such as wearable devices, smart devices, and smart homes, connected to the Internet will enrich our lives.
Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
It is not practical to implement the same TCP/IP protocol stack as a general computer because embedded systems have several restrictions such as low memory capacity.

@@

An approach to improve software productivity is component-based development, which is a design technique that can be applied to reusable software development for embedded systems \cite{par:Crnkovic}\cite{par:CBD}, such as TECS \cite{par:TECS} \cite{par:hr-tecs}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.
In addition, individual component diagrams enable the visualization of an entire system.

This paper proposes component-based TCP/IP protocol stack, i.e., TINET+TECS, to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.

In addition, the proposed framework utilizes dynamic connection, a novel method of TECS, to switch component bindings dynamically.
A general TCP/IP protocol server dynamically processes the requested port i.e., HTTP (port: 80), HTTPS (prot: 443).
However, embedded systems can not dynamically generate components due to the strict memory restriction.
TINET+TECS statically generates components, and dynamically combines them.
Therefore,

In the proposed framework, software application can be developed by not only TECS method but also existing method.
Software appication can be developed as a TECS component because TINET+TECS is a component-based framework using TECS.
Moreover, TECS supports an adapter to call functions of TECS components from non TECS codes.
The legacy codes such as an existing application can be supported in the proposed framework.

This paper evaluates the overheads of execution time and memory consumption and the amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.

@@

    \item {\bf Improve configurability}\mbox{}\\
        Since TINET+TECS is a component-based system, the software is flexible to change the configuration such as resizing network buffer, adding/removing TCP (or UDP) functions, and supporting both IPv4 and IPv6.
        In addition, a component diagram provides visualization of TINET, a complicated system.

    \item {\bf Dynamic connection method}\mbox{}\\
        Dynamically switching the binding of components, that is switching between a communication endpoint and reception point of TINET, realizes a TCP/IP protocol stack for embedded systems.

    \item {\bf Support legacy codes}\mbox{}\\
        TINET+TECS can be applied to an existing application because TECS supports the adapter to call TECS functions from C codes. 
    % \item {\bf Software visualization}

@@

This section describes system model, including the basic technologies such as TINET and TECS.
System model of the proposed framework is shown as Fig. \ref{fig:SystemModel}.
TINET+TECS is a component-based TCP/IP protocol stack, so TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
CEP and REP (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings by TECS method.
Moreover, TECS adapter supports the legacy codes such as an existing application.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/SystemModel.pdf}
    \caption{System model}
    \label{fig:SystemModel}
\end{figure}

\subsection{TINET}
\label{sec:TINET}

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a realtime operating system (RTOS) developed by TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
TINET has been released as open source.

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.
Fig. \ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
% TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
Users transmit and receive the data using a Communication End Point (CEP) which is an interface like a socket.
In transmission process, headers are attached to the data body passed to the CEP at each protocol layer, and the data is transmitted from the network device.
In reception process, headers of the data body received in the network device are analyzed at each protocol layer, and the data is passed to the CEP.

A TCP reception point called Reception Point (REP) is prepared to wait for a connection request from the partner side.
An REP has an IP address ({\it myaddr}) and a port number ({\it myportno}) as attributes, and performs functions like {\it bind()} and {\it listen()}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/ComponentDiagram.pdf}
    \caption{Component Diagram}
    \label{fig:ComponentDiagram}
\end{figure}

@@

Fig. \ref{fig:ComponentDiagram} shows a component diagram.
A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sIPv4Output (Fig. \ref{src:signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in], [out], and [inout] are used, which represent input, output, and input/output respectively.
        [size\_is({\it len})] represents an array of size {\it len}.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sIPv4Output {
  T_IN4_ADDR getIPv4Address(void);
  ER         getOffset([inout]T_OFF_BUF *offset);
  ER         setHeader([inout,size_is(size)]
                        int8_t *outputp,
                        [in]int32_t size,
                        [in]T_IN4_ADDR dstaddr,
                        [in]T_IN4_ADDR srcaddr);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description}
\label{src:signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tIPv4Output (Fig. \ref{src:celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sIPv4Output, and an {\it entry} port name, e.g., eIPv4Output, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tIPv4Output {
    /* Entry port */
    entry sIPv4Output eOutput;

    /* Call port */
    call sEthernetOutput cEthernetOutput;
    /* Omit: other call ports */

    attr {  /* Attribute */
        uint16_t fragInit = 0;
    };
    var {   /* Variable */
        uint16_t fragId = fragInit;
    };
};
\end{lstlisting}
\caption{Celltype description}
\label{src:celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Fig. \ref{src:build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tIPv4Output and IPv4Output, respectively, follow the keyword {\it cell}.
        A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
        In Fig. \ref{src:build}, {\it entry} port eIPv4Output in {\it cell} IPv4Output is connected to {\it call} port cIPv4Output in {\it cell} TCPOutput.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tIPv4Output IPv4Output {
    /* Omit: other build description */

    fragInit = 0; /* Attribute */
};
cell tTCPOutput TCPOutput {
    cIPv4Output = IPv4Output.eOutput;
    /* Omit: other build description */
};
\end{lstlisting}
\caption{Build description}
\label{src:build}
\end{figure}

@@

\subsubsection{Memory allocator component}

The original TINET eliminates dynamic memory control to meet the sever memory restriction of embedded systems.
A memory area for sending/receiving data in the protocol stack is allocated and released within an predetermined area.
Memory allocator component performs the elimination of dynamic memory control in TINET+TECS.
The component provides a requested memory area from the memory area statically allocated.

The memory allocator component connects to as many tFixedSizeMemoryPool as needed, shown as Fig. \ref{fig:tMemoryAllocator}.
tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 to alloc and release a memory area of the requested size. 
tFixedSizeMemoryPool components with various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
On the other hands, all components which need allocate and deallocate memory connect to the memory allocator component, e.g., tTCPInput and tEthernetOutput.

In addition, TINET+TECS utilizes {\it send/receive} specifier of TECS to minimize the memory copy frequency, which is a functionality supported by TINET.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

{\bf send/receive specifier:}
TECS supports {\it send}/{\it receive} specifiers, which are interface specifiers \cite{par:RPC}.
TINET+TECS uses {\it send} and {\it receive} specifiers instead of {\it in} and {\it out} to reduce the number of copies.

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp,
    [in]int32_t size,
    [in]uint8_t align);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp,
    [out]int32_t *size,
    [in]uint8_t align);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{An example of send and receive}
\label{src:SendReceive}
\end{figure}

\subsubsection{Network timer component}

\subsection{Dynamic Connection of TECS}
\label{sec:DynamicConnection}

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

TECS supports dynamic connection method as a novel functionality.
Dynamic connection is a method to switch the binding of components at runtime as shown in Fig. \ref{fig:DynamicConnection}.
Note that all components are statically generated in TECS.
TECS can optimize the overhead of componentization because components are statically configured.
Dynamically generating the components causes a lot of memory consumption, which is a serious propoblem for embedded systems with strict memory constraint.
The proposed framework realizes the componentization of TINET while satisfying the memory constraint, because components statically generate and dynamically connect in TECS.

TINET+TECS utilizes the dynamic connection to swith between CEP and REP components as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state waiting for connection request from clients\footnote{ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}\\tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout)}.
For example, when processing with HTTP protocol, CEP passively opens with REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \caption{Dynamic connection between CEP and REP}
    \label{fig:DynamicConnectionUseCase}
\end{figure}

To utilize dynamic connection, the selector should be defined.
The selector connects all the components that can be dynamically connnected, to refer the descripter of them.
Descriptor is an identifier to access the component.
cREP ports are call ports array, which connect the number of tREP cells (Line 9 in Fig. \ref{src:DynamicCDLcode}).
{\it [ref\_desc]} is described to identify the call port refers to descriptors. 
In the case of Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.

A CEP component has two call ports.
cRepSelector port connects eRepSelector port of tRepSelector cell and cREP4 port connects either of tREP cells (Lines 13-15 in Fig. \ref{src:DynamicCDLcode}).
cREP port is defined with {\it [dynamic]} to identify the call port dynamically switch the components.
The call port with {\it [dynamic]} specifier is not optimized and allocated in RAM by a plug-in.

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sRepSelector {
    void  getRep([out]Descriptor(sREP4) *desc,
                 [in]int_t i);
};

celltype tRepSelector {
    entry sRepSelector eRepSelector;
    [ref_desc]
        call sREP4 cREP[NUM_REP];
};

celltype tTCPCEP {
    call sRepSelector cRepSelector;
    [dynamic]
        call sREP4 cREP;
    /* Omit: other call/entry ports */
    /* Omit: attributes and variables */
};
\end{lstlisting}
\caption{Signature and celltype description for dynamic connection}
\label{src:DynamicCDLcode}
\end{figure}

Fig. \ref{src:DynamicCcode} shows a sample code of dynamic connection.
The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} with TECS, which is utilized to be the state waiting for connection request.
In the function, dynamic connection is performed as shown in Fig. \ref{src:DynamicCcode}.
First, get the descriptor of REP to be joined (Line 3 in Fig. \ref{src:DynamicCcode}).
The first argument, {\it \&desc}, is a variable to store the descriptor information, and the second argument, {\it repid}, is the index of tREP cells.
Next, set the desctriptor (Line 5 in Fig. \ref{src:DynamicCcode}).
cREP port combines the tREP cell that descriptor specify.
Thus, the tCEP cell can call the function of tREP cell to be joined (Line 7 in Fig. \ref{src:DynamicCcode}).

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descripter of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descripter */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\caption{Accept function (a dynamic connection example)}
\label{src:DynamicCcode}
\end{figure}

\subsection{TECS Adapter}
\label{sec:TECS Adapter}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=7.0cm,clip]{figure/TECS_Adapter.pdf}
    \caption{TECS Adapter}
    \label{fig:TECS_Adapter}
\end{figure}

\section{Evaluation}
\label{sec:Evaluation}

@@

Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP}, lwIP \cite{par:lwIP}.

@@

In the future, the proposed framework will cooperate with mruby on TECS \cite{par:mrubyonTECS}.
Note that mruby is a scripting language for embedded systems \cite{par:mruby}.
We will support the functionality that TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.

@@

The authers would like to thank Hiroaki Nagashima for supporting this research.
This work is supported by JSPS KAKENHI Grant Number 15H05305.
